Online {\IterComp}

### 2017-09-15 results.tex
experimental results part 1

In this section we evaluate the performance overhead incurred by the work efficiency profiling.
We measure the wall-clock time of the benchmarks when compiled with the {\flagstype -O3} optimization.
For each benchmark, we compute the average overhead over all its 1,000 inputs.
Figure~\ref{fig:overhead-O3} shows the performance overhead imposed by the work
profiling with each one of the instrumentation strategies, compared to their
non-instrumented counterparts.
The WPO relaxation was performed using profiling information for every specific
input, which provides the perfect information to perform the WPO relaxation.
This means that the experiments show its best performance enabled by having
perfect profiling information.

@@

While the optimal profiling has a maximum overhead of almost 60\%,
the work profiling with a relaxation of 5\% threshold has an overhead of less
than 16\% for all benchmarks,
with the WPO relaxation reaching an average overhead of only 5\%,
compared to an average of 12\% for the optimal profiling.

@@

The most critical case, amongst the evaluated benchmarks, happens with the
\texttt{adpcm\_d} program, with an overhead of about 59\% for the optimal
instrumentation.
With a threshold of only 5\%, the relaxation reduces
the overhead by a factor of $4.5\times$ over the optimal instrumentation,
and the WPO relaxation by a factor of $4.8\times$.
This benchmark has a single hot function
which consists mainly of a single hot loop with several branches inside it. %, as depicted by Figure~\ref{fig:adpcm_d-cfg-instr}.
Most of the improvement achieved by both strategies comes from removing only two
probes from the hot loop.
The two relaxed probes were placed in branches with a high probability of being
taken (above 55\% probability), but with a small contribution to the total amount
of work measured in DAG for this loop (both probes with an static error of
about 1.3\%).
Because these probes were placed in basic blocks with a considerable execution
frequency, their removal resulted in a significant reduction in performance
overhead.

@@

\subsection{Evaluation of the Online {\IterComp}}

>>>>

In this experiment we evaluate the runtime overhead introduced by the work efficiency profiling. We compile the program using the
{\flagstype -O3}. We then measure the wall-clock time of the instrumented and the native versions to calculate the runtime overhead. For
each benchmark, we compute the average overhead over all its 1,000 inputs.

Figure~\ref{fig:overhead-O3} shows the runtime overhead imposed by the work profiling using each of the instrumentation strategies over
their non-instrumented counterparts. The WPO relaxation was performed using profiling information for every specific input, which provides
the perfect information to perform the WPO relaxation. This means that the experiments show its best performance enabled by having perfect
profiling information.

@@

While the optimal profiling has a maximum overhead of near 60\%, the work profiling with a relaxation of 5\% threshold has an overhead of
less than 16\% for all benchmarks, with the WPO relaxation reaching an average overhead of only 5\%, compared to an average of 12\% for the
optimal profiling.

@@

The most critical case, amongst the evaluated benchmarks, happens with the
\texttt{adpcm\_d} program, with an overhead of about 59\% for the optimal
instrumentation.
With a threshold of only 5\%, the relaxation reduces
the overhead by a factor of $4.5\times$ over the optimal instrumentation,
and the WPO relaxation by a factor of $4.8\times$.
This benchmark has a single hot function
which consists mainly of a single hot loop with several branches inside it. %, as depicted by Figure~\ref{fig:adpcm_d-cfg-instr}.
Most of the improvement achieved by both strategies comes from removing only two probes from the hot loop. The two relaxed probes were
placed in branches with a high probability of being taken (above 55\% probability), but with a small contribution to the total amount of
work measured in DAG for this loop (both probes with an static error of about 1.3\%). Because these probes were placed in basic blocks with
a considerable execution frequency, removing the probes resulted in a significant reduction in runtime overhead.

@@

\subsection{Evaluation of Online {\IterComp}}
